Age-related changes in plant growth and traits

### 2015-05-12 results_best.Rmd
forgot to save final changes before

#Working to get counts out of Konrad's reproduction data
```{r, echo=FALSE, message=FALSE}
tmp <- BAER_Investment
FD <- as.data.frame(tmp$FD)
BAER_count <- FD %>%
  group_by(Individual, what) %>%
  summarise_each(funs(sum), count, weight)
BAER_count <- subset(BAER_count, count!=0)
BAER_count$species <- "BAER"

@@

##haven't continued with remaining species, because of problems described
accessory_count <- rbind(BAER_count,BOLE_count,COER_count,EPMI_count,GRBU_count,GRSP_count)
```

>>>>

#getting counts out of Konrad's reproduction data
```{r, echo=FALSE, message=FALSE}
tmp <- BAER_Investment
FD <- as.data.frame(tmp$FD)
BAER_count <- FD %>%
  group_by(Individual, what) %>%
  summarise_each(funs(sum), count, weight)
BAER_count <- subset(BAER_count, count!=0)
BAER_count$species <- "BAER"

@@

tmp <- HATE_Investment
FD <- as.data.frame(tmp$FD)
HATE_count <- FD %>%
  group_by(Individual, what) %>%
  summarise_each(funs(sum), count, weight)
HATE_count <- subset(HATE_count, count!=0)
HATE_count$species <- "HATE"

tmp <- HEPU_Investment
FD <- as.data.frame(tmp$FD)
HEPU_count <- FD %>%
  group_by(Individual, what) %>%
  summarise_each(funs(sum), count, weight)
HEPU_count <- subset(HEPU_count, count!=0)
HEPU_count$species <- "HEPU"

tmp <- LEES_Investment
FD <- as.data.frame(tmp$FD)
LEES_count <- FD %>%
  group_by(Individual, what) %>%
  summarise_each(funs(sum), count, weight)
LEES_count <- subset(LEES_count, count!=0)
LEES_count$species <- "LEES"

tmp <- PELA_Investment
FD <- as.data.frame(tmp$FD)
PELA_count <- FD %>%
  group_by(Individual, what) %>%
  summarise_each(funs(sum), count, weight)
PELA_count <- subset(PELA_count, count!=0)
PELA_count$species <- "PELA"

tmp <- PEPU_Investment
FD <- as.data.frame(tmp$FD)
PEPU_count <- FD %>%
  group_by(Individual, what) %>%
  summarise_each(funs(sum), count, weight)
PEPU_count <- subset(PEPU_count, count!=0)
PEPU_count$species <- "PEPU"

tmp <- PHPH_Investment
FD <- as.data.frame(tmp$FD)
PHPH_count <- FD %>%
  group_by(Individual, what) %>%
  summarise_each(funs(sum), count, weight)
PHPH_count <- subset(PHPH_count, count!=0)
PHPH_count$species <- "PHPH"

tmp <- PILI_Investment
FD <- as.data.frame(tmp$FD)
PILI_count <- FD %>%
  group_by(Individual, what) %>%
  summarise_each(funs(sum), count, weight)
PILI_count <- subset(PILI_count, count!=0)
PILI_count$species <- "PILI"

tmp <- PUTU_Investment
FD <- as.data.frame(tmp$FD)
PUTU_count <- FD %>%
  group_by(Individual, what) %>%
  summarise_each(funs(sum), count, weight)
PUTU_count <- subset(PUTU_count, count!=0)
PUTU_count$species <- "PUTU"

accessory_count <- rbind(BAER_count,BOLE_count,COER_count,EPMI_count,GRBU_count,GRSP_count,HATE_count,HEPU_count,LEES_count,PELA_count,PEPU_count,PHPH_count,PILI_count,PUTU_count)
```
